---
title: "Synth reporting"
author: "Andrew Baxter"
date: "10/09/2019"
output: 
  # pdf_document:
  #   fig_height: 5
  #   fig_width: 8
  #   toc: true
  #   toc_depth: 2
  #   number_sections: true
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
    toc_float:
      collapsed: false
  # word_document:
  #   fig_height: 6
  #   fig_width: 8
  #   reference_docx: report_template.docx
always_allow_html: yes
params:
  save_graphs:
    label: "Save graphs (as svg):"
    value: FALSE
  plotly_graphs:
    label: "Display graphs as plotly (not available in .docx):"
    value: image
    input: radio
    choices: [plotly, image, animate]
  publish_plotly:
    label: "Publish plotly graphs:"
    value: FALSE
header-includes:
   - \usepackage{animate}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	error = FALSE,
	fig.height = 4,
	fig.width = 6,
	message = FALSE,
	warning = FALSE,
	dpi = 150,
	out.width = "100%"
)
library(readxl)
library(tidyverse)
library(stringr)
library(broom)
library(magrittr)
library(Synth)
library(Rcpp)
library(purrr)
library(svglite)
library(SPHSUgraphs)
library(plotly)
library(knitr)
library(gganimate)
`-.gg` <- function(e1, e2) e2(e1)
```
```{r load_functions, include=FALSE}
load('Data/synth_data_b.rdata') # outputted from 'Synth_data.R'
load("Data/filtered_itsp.rdata")  # outputted from 'Synth_create_sps.R'
load("Data/placebo_country_b.rdata")  # outputted from 'Synth_create_sps.R'
load("Data/time_placebos_b.rdata")  # outputted from 'Synth_time_pbs.R'
source('R/Synth_functions.R')
```
```{r results='asis'}
cat("
<style>
caption {
      color: black;
      font-weight: bold;
      font-size: 1.0em;
    }
</style>
")

```

# Setting up data

Data from Human Mortality Database and Human Fertility Database was used to calculate birth rates. This was tidied to give Under-18 rates:

```{r tidy_u18}
kable(head(synthData_u18_filt %>% mutate_if(is.numeric, ~ round(.,2))))
```

Abortion estimates were added to give Under-20 rates:

```{r tidy_u_19}
kable(head(synthData_u20_filt %>% mutate_if(is.numeric, ~ round(.,2))))
```

## Removing non-fitting countries

Several countries were removed (detail added later).

# Iterating through year combinations

For each comparison, I iterated through all combinations of years as special predictors to minimise MSPE (whilst prioritising fewest groupings). For example, for the under-18 basic model with years as special predictors:

```{r example_iterations, eval = FALSE, echo = TRUE}
it_u18_sp <- testSynthIterations(
  yrs = 1990:1998,
  pred = "rate",
  data = synthData_u18[,1:4],
  ccodes = u_18_ccodes,
  n = 4,
  predictors = NULL,
  time.optimise = 1985:1998
) %>%
  arrange(groups, mspe)
```

# Generating Synthetic Control models for all Under-18 comparisons

## Model 1: Rate only as predictor

### England vs Synthetic Control
```{r md_u18_sp, include = FALSE}
opt_y1 <- 1990
synthPrep(synthData_u18_filt[,1:4],
          grp = "u18_sp",
          dependent = "rate",
          special.predictors = sp_u18_filt,
          time.optimise.ssr = opt_y1:1998,
          time.predictors.prior = opt_y1:1998,
          time.plot = opt_y1:2013
          )
```

Over the period 1999 to 2013, England and Wales saw a difference of `r rateDiff(md_u18_sp, "under 18")$tot_diff` births.

```{r md_u18_sp_graph}
gr_u18_sp <- gg_synth(md = md_u18_sp, post = TRUE) 


gr_u18_sp #+ labs(title = sPredText(dp_u18_sp))

if (params$save_graphs){ggsave("graphs/Synth-u18-sp.svg", width = 200, height = 150, units = "mm")}

```

### Weights and balance

```{r st_u18_sp_w}
st_u18_sp$tab.w %>% arrange(desc(w.weights)) %>% select(Country = unit.names, Weight = w.weights) %>% 
  kable(caption = "Country weights")

st_u18_sp$tab.v %>% kable(caption = "Predictor weights")

st_u18_sp$tab.pred %>% kable(caption = "Predictor balance between synthetic and treated units")
```


### Placebo testing by country and time

```{r plot_u18_pb_nat}
pb_plot <- 
  gg_gaps(md_u18_sp, pl_u18_filt) #+ 
  # theme(text = element_text(size = 12),
  #       title = element_text(size = 12)) +
  # labs(title = "England vs Synthetic Control, no added predictors - country placebo")

if (params$plotly_graphs == "plotly"){
  ggplotly(pb_plot)
} else {
pb_plot
}
# api_create(filename = "Plot 43")
```
```{r pp_u18_sp}

pp_u18_sp <- gg_pre_postMSPE(md_u18_sp, pl_u18_filt) + labs(title = "Post/pre-TPS mean squared prediction error")
pp_u18_sp

```

```{r save_u18_pb_nat, include=FALSE}
if (params$save_graphs){ggsave(plot = pp_u18_sp, "graphs/Synth-u18-sp-pp-ratio.svg", width = 200, height = 150, units = "mm")}
 if (params$save_graphs){ggsave(plot = pb_plot, "graphs/Synth-u18-sp-gaps.svg", width = 200, height = 150, units = "mm")}
```

```{r u18_pb_time_graph, fig.show="animate",	interval = 1/20}
tp_u18_sp <- super_md_u18_filt %>% 
  ggplot(aes(Year, Rate, col = Group, linetype = Group, frame = IntYr)) +
  geom_segment(aes(x = IntYr-0.5, xend = IntYr-0.5, y = 0, yend = 20), linetype = "dotted", size = 1, col = "grey", alpha = 0.7) +
  geom_line(size = 1.5) +
  theme_sphsu_light() +
  ylab(paste0("Under-18 birth rate (per 1,000 women)")) +
  theme(legend.title = element_blank(),
        panel.grid = element_blank(),
        line = element_blank()) +
  scale_linetype_manual(name = "Data", values = c("Synthetic" = "solid", "Treated" = "solid")) +
  scale_colour_manual(name = "Data", values = c("Synthetic" = sphsu_cols("Turquoise", names = FALSE), "Treated" = sphsu_cols("Thistle", names = FALSE))) +
  labs(title = "England vs Synthetic Control, no added predictors - time placebo") +
  scale_y_continuous(limits = c(0, 20))

# tp_u18_sp + facet_wrap(super_md_u18_sp$IntYr, ncol = 3)
if (params$plotly_graphs == "plotly") {
tp_u18_sp_plotly <- ggplotly(tp_u18_sp) %>% 
  animation_slider(currentvalue = list(prefix = "Year ", font = list(color="black"))) %>% 
  animation_opts(easing = 'sin-in-out')

return(tp_u18_sp_plotly)
} else if (params$plotly_graphs == "animate"){
  plt <- tp_u18_sp +
    transition_states(IntYr)
  return(plt)
} else {
  tp_u18_sp +
    facet_wrap(~IntYr)
}
#  api_create(tp_u18_sp_plotly, filename = "England under-18 - special predictors - placebo time")

```

# Generating Synthetic Control models for all Under-20 comparisons

## Model 2: England vs Synthetic Control

### England vs Synthetic Control
```{r u20_sp, include = FALSE}
opt_y1 <- 1990
# dataprep and synth
synthPrep(synthData_u20_filt[,1:4],
          "u20_sp",
          dependent = "pRate",
          special.predictors = sp_u20_filt,
          time.optimise.ssr = opt_y1:1998,
          time.predictors.prior = opt_y1:1998,
          time.plot = opt_y1:2013
          )
```

Over the period 1999 to 2013, England and Wales saw a difference of `r rateDiff(md_u20_sp, "under 20")$tot_diff` pregnancies.

```{r md_u20_sp_graph}
# graph
gr_u20_sp <- gg_synth(md = md_u20_sp, post = TRUE) 


gr_u20_sp# + labs(title = sPredText(dp_u20_sp))
 if (params$save_graphs){ggsave("graphs/Synth-u20-sp.svg", width = 200, height = 150, units = "mm")}
```

### Weights and balance
```{r st_u20_sp_w}
# weights kable
st_u20_sp$tab.w %>% arrange(desc(w.weights)) %>% select(Country = unit.names, Weight = w.weights) %>% 
  kable(caption = "Country weights")

st_u20_sp$tab.v %>% kable(caption = "Predictor weights")

st_u20_sp$tab.pred %>% kable(caption = "Predictor balance between synthetic and treated units")
```

### Placebo testing by country and time
```{r plot_u20_sp_pb_nat}
# gaps graph
pb_plot <- 
gg_gaps(md_u20_sp, pl_u20_filt)# + 
  #labs(title = "England vs Synthetic Control, no added predictors - country placebo")

if (params$plotly_graphs == "plotly"){
  ggplotly(pb_plot)
} else {
pb_plot
}

#  api_create(filename = "Plot 49")
```
```{r pp_u20_sp}

pp_u20_sp <- gg_pre_postMSPE(md_u20_sp, pl_u20_filt) + labs(title = "Post/pre-TPS mean squared prediction error")
pp_u20_sp

```
```{r save_u20_sp_pb_nat, include=FALSE}
if (params$save_graphs){ggsave(plot = pp_u20_sp, "graphs/Synth-u20-sp-pp-ratio.svg", width = 200, height = 150, units = "mm")}
 if (params$save_graphs){ggsave(plot = pb_plot, "graphs/Synth-u20-sp-gaps.svg", width = 200, height = 150, units = "mm")}
```


```{r u20_sp_pb_time_graph, fig.show = 'animate', 	interval = 1/20}
# placebo graph
tp_u20_sp <- super_md_u20_filt %>% 
  ggplot(aes(Year, Rate, col = Group, linetype = Group, frame = IntYr)) +
  geom_segment(aes(x = IntYr-0.5, xend = IntYr-0.5, y = 0, yend = 80), linetype = "dotted", size = 1, col = "grey", alpha = 0.7) +
  geom_line(size = 1.5) +
  theme_sphsu_light() +
  ylab(paste0("Under-20 pregnancy rate (per 1,000 women)")) +
  theme(legend.title = element_blank(),
        panel.grid = element_blank(),
        line = element_blank()) +
  scale_linetype_manual(name = "Data", values = c("Synthetic" = "solid", "Treated" = "solid")) +
  scale_colour_manual(name = "Data", values = c("Synthetic" = sphsu_cols("Turquoise", names = FALSE), "Treated" = sphsu_cols("Thistle", names = FALSE))) +
    labs(title = "England vs Synthetic Control, no added predictors - time placebo") +
  scale_y_continuous(limits = c(0, 80))


if (params$plotly_graphs == "plotly") {
  tp_u20_sp_plotly <- ggplotly(tp_u20_sp) %>% 
  animation_slider(currentvalue = list(prefix = "Year ", font = list(color="black"))) %>% 
  animation_opts(easing = 'sin-in-out')
  
  return(tp_u20_sp_plotly)
} else if (params$plotly_graphs == "animate"){
  plt <- tp_u20_sp +
    transition_states(IntYr)
  return(plt)
} else {
  tp_u20_sp + facet_wrap(~ IntYr)
}
#  api_create(tp_u20_sp_plotly, filename = "England under-20 - special predictors - placebo time")
```
