---
title: "Model-testing iterations"
author: "Andrew Baxter"
date: "`r Sys.Date()`"
output:
  # html_document
  word_document:
    fig_height: 6
    fig_width: 8
    reference_docx: C:\Users\2286432b\OneDrive - University of Glasgow\Teenage pregnancy - docs in development\ITS and Synth paper files\Appendices.docx
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, fig.width = 10, fig.height = 6, dpi = 300)

library(dplyr)
library(svglite)
library(tidyr)
library(ggplot2)
library(SPHSUgraphs)
library(purrr)
library(ggrepel)
load('Data/synth_data_c.rdata') # outputted from 'Synth_data.R'
load("Data/filtered_itsp.rdata")  # outputted from 'Synth_create_sps.R'
load("Data/iterating_rm_countries_filt.rdata")
source('R/Synth_functions.R')
# `-.gg` <- function(e1, e2) e2(e1)
```


## Under-18 pregnancy - no added predictors

Plotting MSPEs by iteration and gaps for all iterations.

```{r it_u18_plots}
gr_it_u18_filt <- plotIterations(it_u18_filt)  %>% annotate_figure(top = text_grob("Under-18, no predictors - year iterations"))
gr_it_u18_filt
```

### Top countries

Differing iterations produced different country weightings. I exctracted the top country for each iteration and plotted the lowest MSPE for the top four countries:

```{r it_u18_tops}
gr_tops_u18_filt <- plotIterations(it_u18_filt, labels = TRUE)  %>% annotate_figure(top = text_grob("Under-18, no predictors - year iterations"))
gr_tops_u18_filt
```

### Removing top countries

A further iterative cycle constructed sequential synthetic controls, removing the previous top-weighted country to test for over-reliance on very few abnormal countries. Labels represent the top-weighted country in each analysis by weight and pre-intervention MSPE:

```{r itco_u18_sp}
gr_itco_u18_filt <- gg_iterateCountries(itco_u18_filt, float_labs = TRUE)
gr_itco_u18_filt
```

<!-- ### Removing countries sequentially -->

```{r it_u18_sing_plot, include = FALSE}
df <- it_u18_all_sing %>% 
  # mutate(top_w = map_chr(weights, ~ 
  #          arrange(.x, desc(w.weights)) %>% 
  #          head(1) %>% 
  #            mutate(unit.names = as.character(unit.names)) %>% 
  #          pull(unit.names)))
  unnest(gaps) %>% 
  mutate(mspe = signif(mspe, 2),
         label = ifelse(Year == 2013, paste0(removed, " removed; MSPE = ", mspe), NA))

df %>% 
      ggplot(aes(Year, Gap)) + 
    geom_line(size = 1, aes(col = removed)) + 
    theme_minimal() +
    theme(panel.grid = element_blank()) +
    geom_vline(xintercept = 1998.5, linetype = "dashed", col = "grey") +
    geom_segment(x = 1990, xend = 2013, y = 0, yend = 0, col = "black") +
    scale_colour_sphsu(name = "Country removed") +
    ylab("Gap = Treated - Synthetic Control") +
      theme(legend.position = "none") +
      coord_cartesian(clip = "off") +
      geom_text_repel(aes(x = Year, y = Gap, label = label),
                      hjust = 0,
                      direction = "y",
                      nudge_x = 0.8,
                      xlim = c(NA, 2030)
      ) +
      theme(plot.margin = unit(c(0,10,0,0), "cm"))

```


## Under-20 - no added predictors

```{r it_u20_plots}
gr_it_u20_filt <- plotIterations(it_u20_filt)  %>% annotate_figure(top = text_grob("Under-20, no predictors - year iterations"))
gr_it_u20_filt
```

### Top Countries

```{r it_u20_tops}
gr_tops_u20_filt <- plotIterations(it_u20_filt, labels = TRUE)  %>% annotate_figure(top = text_grob("Under-20, no predictors - year iterations"))
gr_tops_u20_filt
```

### Removing Top Countries

```{r itco_u20_filt}
gr_itco_u20_filt <- gg_iterateCountries(itco_u20_filt, float_labs = TRUE)
gr_itco_u20_filt
```

<!-- ### Removing countries sequentially -->

```{r it_u20_sing_plot, include = FALSE}
df <- it_u20_all_sing %>% 
  # mutate(top_w = map_chr(weights, ~ 
  #          arrange(.x, desc(w.weights)) %>% 
  #          head(1) %>% 
  #            mutate(unit.names = as.character(unit.names)) %>% 
  #          pull(unit.names)))
  unnest(gaps) %>% 
  mutate(mspe = signif(mspe, 2),
         label = ifelse(Year == 2013, paste0(removed, " removed; MSPE = ", mspe), NA))

df %>% 
      ggplot(aes(Year, Gap)) + 
    geom_line(size = 1, aes(col = removed)) + 
    theme_minimal() +
    theme(panel.grid = element_blank()) +
    geom_vline(xintercept = 1998.5, linetype = "dashed", col = "grey") +
    geom_segment(x = 1990, xend = 2013, y = 0, yend = 0, col = "black") +
    scale_colour_sphsu(name = "Country removed") +
    ylab("Gap = Treated - Synthetic Control") +
      theme(legend.position = "none") +
      coord_cartesian(clip = "off") +
      geom_text_repel(aes(x = Year, y = Gap, label = label),
                      hjust = 0,
                      direction = "y",
                      nudge_x = 0.8,
                      xlim = c(NA, 2030)
      ) +
      theme(plot.margin = unit(c(0,10,0,0), "cm"))

```