---
title: "Synth reporting"
author: "Andrew Baxter"
date: "27/01/2019"
output: 
  # pdf_document:
  #   fig_height: 5
  #   fig_width: 8
  #   toc: true
  #   toc_depth: 2
  #   number_sections: true
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
    toc_float:
      collapsed: false
  # word_document:
  #   fig_height: 6
  #   fig_width: 8
  #   reference_docx: report_template.docx
always_allow_html: yes
params:
  save_graphs:
    label: "Save graphs (as svg):"
    value: FALSE
  plotly_graphs:
    label: "Display graphs as plotly (not available in .docx):"
    value: image
    input: radio
    choices: [plotly, image, animate]
  publish_plotly:
    label: "Publish plotly graphs:"
    value: FALSE
header-includes:
   - \usepackage{animate}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	error = FALSE,
	fig.height = 4,
	fig.width = 6,
	message = FALSE,
	warning = FALSE,
	dpi = 150,
	out.width = "100%"
)
library(readxl)
library(tidyverse)
library(stringr)
library(broom)
library(magrittr)
library(Synth)
library(Rcpp)
library(purrr)
library(svglite)
library(SPHSUgraphs)
library(plotly)
library(knitr)
library(gganimate)
library(ggrepel)
library(patchwork)

load('Data/synth_data_b.rdata') # outputted from 'Synth_data.R'
load("Data/filtered_itsp.rdata")  # outputted from 'Synth_create_sps.R'
load("Data/placebo_country_b.rdata")  # outputted from 'Synth_create_sps.R'
load("Data/time_placebos_b.rdata")  # outputted from 'Synth_time_pbs.R'
load('Data/noScot.rdata')
load("Data/other_predictors.rdata")
source('R/Synth_functions.R')
```
```{r results='asis'}
cat("
<style>
caption {
      color: black;
      font-weight: bold;
      font-size: 1.0em;
    }
</style>
")

```

# Setting up data

Data from Human Mortality Database and Human Fertility Database was used to calculate birth rates. This was tidied to give Under-18 rates:

```{r tidy_u18}
kable(head(synthData_u18_filt %>% mutate_if(is.numeric, ~ round(.,2))))
```

Abortion estimates were added to give Under-20 rates:

```{r tidy_u_19}
kable(head(synthData_u20_filt %>% mutate_if(is.numeric, ~ round(.,2))))
```

## Removing non-fitting countries

Several countries were removed (detail added later).

# Iterating through year combinations

For each comparison, I iterated through all combinations of years as special predictors to minimise MSPE (whilst prioritising fewest groupings). For example, for the under-18 basic model with years as special predictors:

```{r example_iterations, eval = FALSE, echo = TRUE}
it_u18_sp <- testSynthIterations(
  yrs = 1990:1998,
  pred = "rate",
  data = synthData_u18[,1:4],
  ccodes = u_18_ccodes,
  n = 4,
  predictors = NULL,
  time.optimise = 1985:1998
) %>%
  arrange(groups, mspe)
```

# All countries, no additional predictors

## Model 1: Under-18 birth rates

### All Countries graph

```{r all_u18_rates, fig.width=7.9, fig.height=5.9}

labels <- synthData_u18_filt %>% 
  filter(Year==2013)

gr_u18_rates <- synthData_u18_filt %>% 
  ggplot(aes(Year, rate, col = Country)) +
  geom_line(size = 1) +
  scale_colour_sphsu() +
  theme_minimal() + 
  theme(panel.grid = element_blank(),
        axis.line = element_line(size = 0.1, colour = "grey"),
        axis.line.y = element_blank(),
        legend.position = "none",
        plot.margin = unit(c(0,7,2,0), "cm"),
        text = element_text(family = "sans")) +
  coord_cartesian(clip = "off") +
  geom_text_repel(data = labels,
                  aes(x = Year+0.5,
                      y = rate,
                      label = Country),
                  family = "sans",
                  hjust = 0,
                  nudge_x = 3,
                  direction = "y",
                  xlim = c(NA, 2030),
                  ylim = c(-1, 40),
                  point.padding = 0) +
  ylab("Under-18 birth rate (per 1,000 women)") +
  scale_x_continuous(expand = expand_scale(add = c(0, -1)), limits  = c(1990, 2014)) +
  scale_y_continuous(expand = c(0,0))

# ggsave(gr_u18_rates, "graphs/Under-18 all countries.svg", width = 200, height = 150, units = "mm")

gr_u18_rates
```

### England vs Synthetic Control
```{r md_u18_sp, include = FALSE}
opt_y1 <- 1990
synthPrep(synthData_u18_filt[,1:4],
          grp = "u18_sp",
          dependent = "rate",
          special.predictors = sp_u18_filt,
          time.optimise.ssr = opt_y1:1998,
          time.predictors.prior = opt_y1:1998,
          time.plot = opt_y1:2013
          )
```

Over the period 1999 to 2013, England and Wales saw a difference of `r rateDiff(md_u18_sp, "under 18")$tot_diff` births (to an average population of `r rateDiff(md_u18_sp, "under 18")$mean_pop` women).

```{r md_u18_sp_graph}
gr_u18_sp <- gg_synth(md = md_u18_sp, post = TRUE) 


gr_u18_sp #+ labs(title = sPredText(dp_u18_sp))

if (params$save_graphs){
  
  ggsave("graphs/Synth-u18-sp.svg",
         gr_u18_sp +
           theme(title = element_text(size = 14),
                 axis.title = element_text(size = 12)),
         dpi = 400,
         width = 200, height = 150, units = "mm")
  
  }

```

### Weights and balance

```{r st_u18_sp_w}
st_u18_sp$tab.w %>% arrange(desc(w.weights)) %>% select(Country = unit.names, Weight = w.weights) %>% 
  kable(caption = "Country weights")

st_u18_sp$tab.v %>% kable(caption = "Predictor weights")

st_u18_sp$tab.pred %>% kable(caption = "Predictor balance between synthetic and treated units")
```


### Placebo testing by country and time

```{r plot_u18_pb_nat}
pb_plot_u18_sp <- 
  gg_gaps(md_u18_sp, pl_u18_filt) #+ 
  # theme(text = element_text(size = 12),
  #       title = element_text(size = 12)) +
  # labs(title = "England vs Synthetic Control, no added predictors - country placebo")

if (params$plotly_graphs == "plotly"){
  ggplotly(pb_plot_u18_sp)
} else {
pb_plot_u18_sp
}

if (params$plotly_graphs == "plotly" & params$publish_plotly) {
api_create(last_plot(), filename = "Plot 43")
}

# gr_u18_sp + pb_plot_u18_sp + plot_layout(guides = "collect")
# ((gr_u18_sp +
#       theme(legend.position = "bottom", legend.text = element_text(size = 14)) +
#       ggtitle("a) England and Wales vs Synthetic Control")) |
#     pb_plot_u18_sp +
#     ggtitle("b) Gaps between observed and control, plotted by country")) /
#     guide_area() +
#     plot_layout(guides = "collect", nrow = 2, heights = c(6, 1))
# ggsave("graphs/Synth_u18_sp output.png", width = 300, height = 150, units = "mm", dpi = 500)

```

```{r rank_u18}
pp_u18_sp <- gg_pre_postMSPE(md_u18_sp, pl_u18_filt) + labs(title = "Post/pre-TPS mean squared prediction error")

p18 <- ggplot_build(pp_u18_sp)

rank_u18 <- p18$plot$data %>% 
  arrange(desc(ratio)) %>% 
  ungroup() %>% 
  mutate(rank = rank(-ratio)) %>% 
  select(Country, ratio, rank)
```

In placebo-country tests, England and Wales ranked `r rank_u18 %>% filter(Country == "England and Wales") %>% pull(rank)` out of `r nrow(rank_u18)` countries by pre/post-MSPE ratio.

```{r pp_u18_sp}

pp_u18_sp

```

```{r save_u18_pb_nat, include=FALSE}
if (params$save_graphs){ggsave(
  plot = pp_u18_sp +
           theme(title = element_text(size = 14),
                 axis.title = element_text(size = 12),
                 legend.position = "none"),
         dpi = 400, "graphs/Synth-u18-sp-pp-ratio.svg", width = 200, height = 150, units = "mm"
  )}
 if (params$save_graphs){ggsave(
   plot = pb_plot_u18_sp +
           theme(title = element_text(size = 14),
                 axis.title = element_text(size = 12),
                 legend.position = "none"),  dpi = 400, "graphs/Synth-u18-sp-gaps.svg", width = 200, height = 150, units = "mm")}
```

```{r u18_pb_time_graph, fig.show="animate",	interval = 1/20}
tp_u18_sp <- super_md_u18_filt %>% 
  ggplot(aes(Year, Rate, col = Group, linetype = Group, frame = IntYr)) +
  geom_segment(aes(x = IntYr-0.5, xend = IntYr-0.5, y = 0, yend = 20), linetype = "dotted", size = 1, col = "grey", alpha = 0.7) +
  geom_line(size = 1.5) +
  theme_sphsu_light() +
  ylab(paste0("Under-18 birth rate (per 1,000 women)")) +
  theme(legend.title = element_blank(),
        panel.grid = element_blank(),
        line = element_blank()) +
  scale_linetype_manual(name = "Data", values = c("Synthetic" = "solid", "Treated" = "solid")) +
  scale_colour_manual(name = "Data", values = c("Synthetic" = sphsu_cols("Turquoise", names = FALSE), "Treated" = sphsu_cols("Thistle", names = FALSE))) +
  labs(title = "England vs Synthetic Control, no added predictors - time placebo") +
  scale_y_continuous(limits = c(0, 20))

# tp_u18_sp + facet_wrap(super_md_u18_sp$IntYr, ncol = 3)
if (params$plotly_graphs == "plotly") {
tp_u18_sp_plotly <- ggplotly(tp_u18_sp) %>% 
  animation_slider(currentvalue = list(prefix = "Year ", font = list(color="black"))) %>% 
  animation_opts(easing = 'sin-in-out')

return(tp_u18_sp_plotly)
} else if (params$plotly_graphs == "animate"){
  plt <- tp_u18_sp +
    transition_states(IntYr)
  return(plt)
} else {
  tp_u18_sp +
    facet_wrap(~IntYr)
}

if (params$plotly_graphs == "plotly" & params$publish_plotly) {
 api_create(tp_u18_sp_plotly, filename = "England under-18 - special predictors - placebo time")
}
```

## Model 2: Under-20 pregnancy rates

### All Countries graph

```{r all_u20_rates, fig.width=7.9, fig.height=5.9}

labels <- synthData_u20_filt %>% 
  filter(Year==2013)

gr_u20_rates <- synthData_u20_filt %>% 
  ggplot(aes(Year, pRate, col = Country)) +
  geom_line(size = 1) +
  scale_colour_sphsu() +
  theme_minimal() + 
  theme(panel.grid = element_blank(),
        axis.line = element_line(size = 0.1, colour = "grey"),
        axis.line.y = element_blank(),
        legend.position = "none",
        plot.margin = unit(c(0,7,2,0), "cm"),
        text = element_text(family = "sans")) +
  coord_cartesian(clip = "off") +
  geom_text_repel(data = labels,
                  aes(x = Year+0.5, y = pRate, label = Country),
                  family = "sans",
                  hjust = 0,
                  nudge_x = 3,
                  direction = "y",
                  xlim = c(NA, 2030),
                  ylim = c(-1, 75),
                  point.padding = 0) +
  ylab("Under-20 pregnancy rate (per 1,000 women)") +
  scale_x_continuous(expand = expand_scale(add = c(0, -1)), limits  = c(1990, 2014)) +
  scale_y_continuous(expand = c(0,0))

# ggsave("graphs/Under-20 all countries.svg", gr_u20_rates, width = 200, height = 150, units = "mm")

gr_u20_rates
```

4.27### England vs Synthetic Control
```{r u20_sp, include = FALSE}
opt_y1 <- 1990
# dataprep and synth
synthPrep(synthData_u20_filt[,1:4],
          "u20_sp",
          dependent = "pRate",
          special.predictors = sp_u20_filt,
          time.optimise.ssr = opt_y1:1998,
          time.predictors.prior = opt_y1:1998,
          time.plot = opt_y1:2013
          )
```

Over the period 1999 to 2013, England and Wales saw a difference of `r rateDiff(md_u20_sp, "under 20")$tot_diff` pregnancies (to an average population of `r rateDiff(md_u20_sp, "under 20")$mean_pop` women).

```{r md_u20_sp_graph}
# graph
gr_u20_sp <- gg_synth(md = md_u20_sp, post = TRUE) 


gr_u20_sp# + labs(title = sPredText(dp_u20_sp))
 if (params$save_graphs){ggsave("graphs/Synth-u20-sp.svg", width = 200, height = 150, units = "mm")}


```

### Weights and balance
```{r st_u20_sp_w}
# weights kable
st_u20_sp$tab.w %>% arrange(desc(w.weights)) %>% select(Country = unit.names, Weight = w.weights) %>% 
  kable(caption = "Country weights")

st_u20_sp$tab.v %>% kable(caption = "Predictor weights")

st_u20_sp$tab.pred %>% kable(caption = "Predictor balance between synthetic and treated units")
```


### Placebo testing by country and time
```{r plot_u20_sp_pb_nat}
# gaps graph
pb_plot_u20_sp <- 
gg_gaps(md_u20_sp, pl_u20_filt)# + 
  #labs(title = "England vs Synthetic Control, no added predictors - country placebo")

if (params$plotly_graphs == "plotly"){
  ggplotly(pb_plot_u20_sp)
} else {
pb_plot_u20_sp
}
if (params$plotly_graphs == "plotly" & params$publish_plotly) {
 api_create(last_plot(), filename = "Plot 49")
}

# ((gr_u20_sp +
#       theme(legend.position = "bottom", legend.text = element_text(size = 14)) +
#       ggtitle("a) England and Wales vs Synthetic Control")) |
#     pb_plot_u20_sp +
#     ggtitle("b) Gaps between observed and control, plotted by country")) /
#     guide_area() +
#     plot_layout(guides = "collect", nrow = 2, heights = c(6, 1))
# ggsave("graphs/Synth_u20_sp output.png", width = 300, height = 150, units = "mm", dpi = 500)
```
```{r rank_u20, include=FALSE}
pp_u20_sp <- gg_pre_postMSPE(md_u20_sp, pl_u20_filt) + labs(title = "Post/pre-TPS mean squared prediction error")

p20 <- ggplot_build(pp_u20_sp)

rank_u20 <- p20$plot$data %>% 
  arrange(desc(ratio)) %>% 
  ungroup() %>% 
  mutate(rank = rank(-ratio)) %>% 
  select(Country, ratio, rank)
```

In placebo-country tests, England and Wales ranked `r rank_u20 %>% filter(Country == "England and Wales") %>% pull(rank)` out of `r nrow(rank_u20)` countries by pre/post-MSPE ratio.

```{r pp_u20_sp}

pp_u20_sp

```
```{r save_u20_sp_pb_nat, include=FALSE}
if (params$save_graphs){ggsave(plot = pp_u20_sp, "graphs/Synth-u20-sp-pp-ratio.svg", width = 200, height = 150, units = "mm")}
 if (params$save_graphs){ggsave(plot = pb_plot_u20_sp, "graphs/Synth-u20-sp-gaps.svg", width = 200, height = 150, units = "mm")}
```


```{r u20_sp_pb_time_graph, fig.show = 'animate', 	interval = 1/20}
# placebo graph
tp_u20_sp <- super_md_u20_filt %>% 
  ggplot(aes(Year, Rate, col = Group, linetype = Group, frame = IntYr)) +
  geom_segment(aes(x = IntYr-0.5, xend = IntYr-0.5, y = 0, yend = 80), linetype = "dotted", size = 1, col = "grey", alpha = 0.7) +
  geom_line(size = 1.5) +
  theme_sphsu_light() +
  ylab(paste0("Under-20 pregnancy rate (per 1,000 women)")) +
  theme(legend.title = element_blank(),
        panel.grid = element_blank(),
        line = element_blank()) +
  scale_linetype_manual(name = "Data", values = c("Synthetic" = "solid", "Treated" = "solid")) +
  scale_colour_manual(name = "Data", values = c("Synthetic" = sphsu_cols("Turquoise", names = FALSE), "Treated" = sphsu_cols("Thistle", names = FALSE))) +
    labs(title = "England vs Synthetic Control, no added predictors - time placebo") +
  scale_y_continuous(limits = c(0, 80))


if (params$plotly_graphs == "plotly") {
  tp_u20_sp_plotly <- ggplotly(tp_u20_sp) %>% 
  animation_slider(currentvalue = list(prefix = "Year ", font = list(color="black"))) %>% 
  animation_opts(easing = 'sin-in-out')
  
  return(tp_u20_sp_plotly)
} else if (params$plotly_graphs == "animate"){
  plt <- tp_u20_sp +
    transition_states(IntYr)
  return(plt)
} else {
  tp_u20_sp + facet_wrap(~ IntYr)
}

if (params$plotly_graphs == "plotly" & params$publish_plotly) {
 api_create(tp_u20_sp_plotly, filename = "England under-20 - special predictors - placebo time")
}
```

# Filtered to remove Scotland, no additional predictors

## Model 3: Under-18 birth rates

### England vs Synthetic Control
```{r md_u18_ns, include = FALSE}
opt_y1 <- 1990
synthPrep(sd_noScot,
          grp = "u18_ns",
          dependent = "rate",
          special.predictors = sp_u18_filt,
          time.optimise.ssr = opt_y1:1998,
          time.predictors.prior = 1990:1998,
          time.plot = 1990:2013
          )
```

Over the period 1999 to 2013, England and Wales saw a difference of `r rateDiff(md_u18_ns, "under 18")$tot_diff` births (to an average population of `r rateDiff(md_u18_ns, "under 18")$mean_pop` women).

```{r md_u18_ns_graph}
gr_u18_ns <- gg_synth(md = md_u18_ns, post = TRUE) + xlim(1990, 2013)


gr_u18_ns #+ labs(title = sPredText(dp_u18_ns))

if (params$save_graphs){ggsave("graphs/Synth-u18-ns.svg", width = 200, height = 150, units = "mm")}

```

Loss-V (For optimised period) = `r signif(so_u18_ns$loss.v[[1]], 3)`, MSPE (for whole pre-intervention observation period) = `r pre_MSPE(md_u18_ns)`.

### Weights and balance

```{r st_u18_ns_w}
st_u18_ns$tab.w %>% arrange(desc(w.weights)) %>% select(Country = unit.names, Weight = w.weights) %>% 
  kable(caption = "Country weights")

st_u18_ns$tab.v %>% kable(caption = "Predictor weights")

st_u18_ns$tab.pred %>% kable(caption = "Predictor balance between synthetic and treated units")
```


### Placebo testing by country and time

```{r plot_u18_pb_ns}
pb_plot_u18_ns <- 
  gg_gaps(md_u18_ns, pl_u18_ns) #+ 
  # theme(text = element_text(size = 12),
  #       title = element_text(size = 12)) +
  # labs(title = "England vs Synthetic Control, no added predictors - country placebo")

if (params$plotly_graphs == "plotly"){
  ggplotly(pb_plot_u18_ns)
} else {
pb_plot_u18_ns
}

if (params$plotly_graphs == "plotly" & params$publish_plotly) {
api_create(last_plot(), filename = "Gaps - U18 - Excl Scotland")
}

# ((gr_u18_ns +
#       theme(legend.position = "bottom", legend.text = element_text(size = 14)) +
#       ggtitle("a) England and Wales vs Synthetic Control")) |
#     pb_plot_u18_ns +
#     ggtitle("b) Gaps between observed and control, plotted by country")) /
#     guide_area() +
#     plot_layout(guides = "collect", nrow = 2, heights = c(6, 1))
# ggsave("graphs/Synth_u18_ns output.png", width = 300, height = 150, units = "mm", dpi = 500)

```
```{r rank_u18_ns}
pp_u18_ns <- gg_pre_postMSPE(md_u18_ns, pl_u18_filt) + labs(title = "Post/pre-TPS mean squared prediction error")

p18 <- ggplot_build(pp_u18_ns)

rank_u18 <- p18$plot$data %>% 
  arrange(desc(ratio)) %>% 
  ungroup() %>% 
  mutate(rank = rank(-ratio)) %>% 
  select(Country, ratio, rank)
```

In placebo-country tests, England and Wales ranked `r rank_u18 %>% filter(Country == "England and Wales") %>% pull(rank)` out of `r nrow(rank_u18)` countries by pre/post-MSPE ratio.

```{r pp_u18_ns}

pp_u18_ns

```

```{r save_u18_pb_nat_ns, include=FALSE}
if (params$save_graphs){ggsave(plot = pp_u18_ns, "graphs/Synth-u18-ns-pp-ratio.svg", width = 200, height = 150, units = "mm")}
 if (params$save_graphs){ggsave(plot = pb_plot_u18_ns, "graphs/Synth-u18-ns-gaps.svg", width = 200, height = 150, units = "mm")}
```

```{r u18_pb_time_graph_ns, fig.show="animate",	interval = 1/20}
tp_u18_ns <- super_md_u18_ns %>% 
  ggplot(aes(Year, Rate, col = Group, linetype = Group, frame = IntYr)) +
  geom_segment(aes(x = IntYr-0.5, xend = IntYr-0.5, y = 0, yend = 20), linetype = "dotted", size = 1, col = "grey", alpha = 0.7) +
  geom_line(size = 1.5) +
  theme_sphsu_light() +
  ylab(paste0("Under-18 birth rate (per 1,000 women)")) +
  theme(legend.title = element_blank(),
        panel.grid = element_blank(),
        line = element_blank()) +
  scale_linetype_manual(name = "Data", values = c("Synthetic" = "solid", "Treated" = "solid")) +
  scale_colour_manual(name = "Data", values = c("Synthetic" = sphsu_cols("Turquoise", names = FALSE), "Treated" = sphsu_cols("Thistle", names = FALSE))) +
  labs(title = "England vs Synthetic Control, no added predictors - time placebo") +
  scale_y_continuous(limits = c(0, 20))

# tp_u18_ns + facet_wrap(super_md_u18_ns$IntYr, ncol = 3)
if (params$plotly_graphs == "plotly") {
tp_u18_ns_plotly <- ggplotly(tp_u18_ns) %>% 
  animation_slider(currentvalue = list(prefix = "Year ", font = list(color="black"))) %>% 
  animation_opts(easing = 'sin-in-out')

return(tp_u18_ns_plotly)
} else if (params$plotly_graphs == "animate"){
  plt <- tp_u18_ns +
    transition_states(IntYr)
  return(plt)
} else {
  tp_u18_ns +
    facet_wrap(~IntYr)
}

if (params$plotly_graphs == "plotly" & params$publish_plotly) {
 api_create(tp_u18_ns_plotly, filename = "England under-18 - excl Scotland - placebo time")
}
```

## Model 4: Under-20 pregnancy rates

### England vs Synthetic Control
```{r u20_ns, include = FALSE}
opt_y1 <- 1996
# dataprep and synth
synthPrep(sd_noScot,
          "u20_ns",
          dependent = "pRate",
          special.predictors = sp_u20_filt,
          time.optimise.ssr = opt_y1:1998,
          time.predictors.prior = 1990:1998,
          time.plot = 1990:2013
          )
```

Over the period 1999 to 2013, England and Wales saw a difference of `r rateDiff(md_u20_ns, "under 20")$tot_diff` pregnancies (to an average population of `r rateDiff(md_u20_ns, "under 20")$mean_pop` women).

```{r md_u20_ns_graph}
# graph
gr_u20_ns <- gg_synth(md = md_u20_ns, post = TRUE) + xlim(1990, 2013) 


gr_u20_ns# + labs(title = sPredText(dp_u20_ns))
 if (params$save_graphs){ggsave("graphs/Synth-u20-sp.svg", width = 200, height = 150, units = "mm")}
```

Loss-V (For optimised period) = `r signif(so_u20_ns$loss.v[[1]], 3)`, MSPE (for whole pre-intervention observation period) = `r pre_MSPE(md_u20_ns)`.

### Weights and balance
```{r st_u20_ns_w}
# weights kable
st_u20_ns$tab.w %>% arrange(desc(w.weights)) %>% select(Country = unit.names, Weight = w.weights) %>% 
  kable(caption = "Country weights")

st_u20_ns$tab.v %>% kable(caption = "Predictor weights")

st_u20_ns$tab.pred %>% kable(caption = "Predictor balance between synthetic and treated units")
```


### Placebo testing by country and time
```{r plot_u20_ns_pb_nat}
# gaps graph
pb_plot_u20_ns <- 
gg_gaps(md_u20_ns, pl_u20_ns)# + 
  #labs(title = "England vs Synthetic Control, no added predictors - country placebo")

if (params$plotly_graphs == "plotly"){
  ggplotly(pb_plot_u20_ns)
} else {
pb_plot_u20_ns
}
if (params$plotly_graphs == "plotly" & params$publish_plotly) {
 api_create(last_plot(), filename = "Plot 49")
}


# ((gr_u20_ns +
#       theme(legend.position = "bottom", legend.text = element_text(size = 14)) +
#       ggtitle("a) England and Wales vs Synthetic Control")) |
#     pb_plot_u20_ns +
#     ggtitle("b) Gaps between observed and control, plotted by country")) /
#     guide_area() +
#     plot_layout(guides = "collect", nrow = 2, heights = c(6, 1))
# ggsave("graphs/Synth_u20_ns output.png", width = 300, height = 150, units = "mm", dpi = 500)
```
```{r rank_u20_ns}
pp_u20_ns <- gg_pre_postMSPE(md_u20_ns, pl_u20_ns) + labs(title = "Post/pre-TPS mean squared prediction error")

p20 <- ggplot_build(pp_u20_ns)

rank_u20 <- p20$plot$data %>% 
  arrange(desc(ratio)) %>% 
  ungroup() %>% 
  mutate(rank = rank(-ratio)) %>% 
  select(Country, ratio, rank)
```

In placebo-country tests, England and Wales ranked `r rank_u20 %>% filter(Country == "England and Wales") %>% pull(rank)` out of `r nrow(rank_u20)` countries by pre/post-MSPE ratio.

```{r pp_u20_ns}

pp_u20_ns

```
```{r save_u20_ns_pb_nat, include=FALSE}
if (params$save_graphs){ggsave(plot = pp_u20_ns, "graphs/Synth-u20-sp-pp-ratio.svg", width = 200, height = 150, units = "mm")}
 if (params$save_graphs){ggsave(plot = pb_plot_u20_ns, "graphs/Synth-u20-sp-gaps.svg", width = 200, height = 150, units = "mm")}
```


```{r u20_ns_pb_time_graph, fig.show = 'animate', 	interval = 1/20, include = FALSE}
# placebo graph
tp_u20_ns <- super_md_u20_ns %>% 
  ggplot(aes(Year, Rate, col = Group, linetype = Group, frame = IntYr)) +
  geom_segment(aes(x = IntYr-0.5, xend = IntYr-0.5, y = 0, yend = 80), linetype = "dotted", size = 1, col = "grey", alpha = 0.7) +
  geom_line(size = 1.5) +
  theme_sphsu_light() +
  ylab(paste0("Under-20 pregnancy rate (per 1,000 women)")) +
  theme(legend.title = element_blank(),
        panel.grid = element_blank(),
        line = element_blank()) +
  scale_linetype_manual(name = "Data", values = c("Synthetic" = "solid", "Treated" = "solid")) +
  scale_colour_manual(name = "Data", values = c("Synthetic" = sphsu_cols("Turquoise", names = FALSE), "Treated" = sphsu_cols("Thistle", names = FALSE))) +
    labs(title = "England vs Synthetic Control, no added predictors - time placebo") +
  scale_y_continuous(limits = c(0, 80))


if (params$plotly_graphs == "plotly") {
  tp_u20_ns_plotly <- ggplotly(tp_u20_ns) %>% 
  animation_slider(currentvalue = list(prefix = "Year ", font = list(color="black"))) %>% 
  animation_opts(easing = 'sin-in-out')
  
  return(tp_u20_ns_plotly)
} else if (params$plotly_graphs == "animate"){
  plt <- tp_u20_ns +
    transition_states(IntYr)
  return(plt)
} else {
  tp_u20_ns + facet_wrap(~ IntYr)
}

if (params$plotly_graphs == "plotly" & params$publish_plotly) {
 api_create(tp_u20_ns_plotly, filename = "England under-20 - special predictors - placebo time")
}
```

# Adding all predictors

## Model 5: Under-18 birth rates

### England vs Synthetic Control

```{r u18_all, include = FALSE}

opt_y1 <- 1990
synthPrep(sd_noScot,
          "u18_all",
          dependent = "rate",
          special.predictors = sp_u18_filt %>% 
            append(sp_u20_gdp) %>% 
            append(sp_u20_edu) %>% 
            append(sp_u20_mob) %>% 
            append(sp_u20_urb),
          time.optimise.ssr = opt_y1:1998,
          time.plot = 1990:2013,
          time.predictors.prior = 1990:1998
)

```

```{r md_u18_all_graph}
# graph
gr_u18_all <- gg_synth(md = md_u18_all, post = TRUE)  + xlim(1990, 2013)


gr_u18_all #+ labs(title = sPredText(dp_u18_all))


#  ggsave("graphs/Synth-u18-all-1990.svg", width = 200, height = 150, units = "mm")
```

Loss-V (For optimised period) = `r signif(so_u18_all$loss.v[[1]], 3)`, MSPE (for whole pre-intervention observation period) = `r pre_MSPE(md_u18_all)`.

### Weights and balance
```{r st_u18_all_w}
# weights kable
st_u18_all$tab.w %>% arrange(desc(w.weights)) %>% select(Country = unit.names, Weight = w.weights) %>% 
  kable(caption = "Country weights")

st_u18_all$tab.v %>% kable(caption = "Predictor weights")

st_u18_all$tab.pred %>% kable(caption = "Predictor balance between synthetic and treated units")
```

### Placebo testing by country

```{r plot_u18_pb_all}
pb_plot_u18_all <- 
  gg_gaps(md_u18_all, pl_u18_all) #+ 
  # theme(text = element_text(size = 12),
  #       title = element_text(size = 12)) +
  # labs(title = "England vs Synthetic Control, no added predictors - country placebo")

if (params$plotly_graphs == "plotly"){
  ggplotly(pb_plot_u18_all)
} else {
pb_plot_u18_all
}

if (params$plotly_graphs == "plotly" & params$publish_plotly) {
api_create(last_plot(), filename = "Gaps - U18 - Excl Scotland")
}

```

```{r rank_u18_all}
pp_u18_all <- gg_pre_postMSPE(md_u18_all, pl_u18_all) + labs(title = "Post/pre-TPS mean squared prediction error")

p18 <- ggplot_build(pp_u18_all)

rank_u18 <- p18$plot$data %>% 
  arrange(desc(ratio)) %>% 
  ungroup() %>% 
  mutate(rank = rank(-ratio)) %>% 
  select(Country, ratio, rank)
```

In placebo-country tests, England and Wales ranked `r rank_u20 %>% filter(Country == "England and Wales") %>% pull(rank)` out of `r nrow(rank_u20)` countries by pre/post-MSPE ratio.

```{r pp_u18_all}

pp_u18_all

```

## Model 6: Under-20 pregnancy rates

### England vs Synthetic Control

```{r u20_all, include=FALSE}
opt_y1 <- 1996
synthPrep(sd_noScot,
          "u20_all",
          dependent = "pRate",
          special.predictors = sp_u20_filt %>% 
            append(sp_u20_mob) %>% 
            append(sp_u20_edu) %>% 
            append(sp_u20_gdp) %>% 
            append(sp_u20_urb),
          time.optimise.ssr = 1996:1998,
          time.plot = 1990:2013,
          time.predictors.prior = 1990:1998
)

```

```{r md_u20_all_graph}
gr_u20_all <- gg_synth(md = md_u20_all, post = FALSE) + xlim(1990, 2013)

gr_u20_all
```

Loss-V (For optimised period) = `r signif(so_u20_all$loss.v[[1]], 3)`, MSPE (for whole pre-intervention observation period) = `r pre_MSPE(md_u20_all)`.

### Weights and balance
```{r st_u20_all_w}
# weights kable
st_u20_all$tab.w %>% arrange(desc(w.weights)) %>% select(Country = unit.names, Weight = w.weights) %>% 
  kable(caption = "Country weights")

st_u20_all$tab.v %>% kable(caption = "Predictor weights")

st_u20_all$tab.pred %>% kable(caption = "Predictor balance between synthetic and treated units")
```

<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>