---
title: "Model-testing iterations"
author: "Andrew Baxter"
date: "19/09/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, fig.width = 10)

library(dplyr)
library(svglite)
# library(SPHSUgraphs)
# library(purrr)

`-.gg` <- function(e1, e2) e2(e1)
```

```{r load_data, include = FALSE}
load('Data/synth_data.rdata') # outputted from 'Synth_data.R'
load("Data/iterations.rdata")
load("Data/iterating_rm_countries.rdata")
source('R/Synth_functions.R')
```

# Under-18 pregnancy - no added predictors

```{r it_u18_plots}
gr_it_u18_sp <- plotIterations(it_u18_rateSp)  %>% annotate_figure(top = text_grob("Under-18, no predictors - year iterations"))
gr_it_u18_sp
```

## Top countries

Differing iterations produced different country weightings. I exctracted the top country for each iteration and plotted the lowest MSPE for the top four countries:

```{r it_u18_tops}
gr_it_u18_sp <- plotIterations(it_u18_rateSp, labels = TRUE)  %>% annotate_figure(top = text_grob("Under-18, no predictors - year iterations"))
gr_it_u18_sp
```

## Removing top countries

A further iterative cycle constructed sequential synthetic controls, removing the previous top-weighted country to test for over-reliance on very few abnormal countries:

```{r itco_u18_sp}
order_co <- 
  itco_u18_sp %>% map( ~ select(.x, label)) %>% 
    reduce(bind_rows) %>% 
    pull()

itco_u18_sp %>% 
  reduce(bind_rows) %>% 
  filter(mspe<5*min(mspe)) %>% 
  select(mspe, unit.names, label, gaps) %>% 
  unnest(gaps) %>% 
  mutate(label = factor(label, levels = order_co)) %>% 
  ggplot(aes(Year, Gap)) + 
  geom_line(size = 1, alpha = 0.8, aes(col = label)) + 
  theme_minimal() +
  theme(panel.grid = element_blank()) +
  geom_vline(xintercept = 1998.5, linetype = "dashed", col = "grey") +
  geom_segment(x = 1985, xend = 2013, y = 0, yend = 0, col = "black") +
  scale_colour_sphsu(name = "Top weighted country")

```



